Refactoring `nls()`: a constructive critique

### 2023-02-03 RefactoringNLS/JNAB230203.Rmd
interim output of port etc.

>>>>

### Interim output from the "port" algorithm

As the `nls()` **man** page states, when the "port" algorithm is used with the `trace` argument
TRUE, the iterations display the objective function value which is 1/2 the sum of squares (or 
deviance). It is likely that the trace display is embedded in the Fortran of the `nlminb`
routine that is called to execute the "port" algorithm, but the factor of 2 discrepancy is nonetheless
unfortunate for users.

### Failure to return best result achieved

If `nls()` reaches a point where it cannot continue but has not found a point where the
relative offset convergence criterion is met, it may simply exit, especially if a 
"singular gradient" (singular Jacobian) is found. However, this may occur AFTER the 
function has made considerable progress in reducing the sum of squared residuals. 
<!-- An example is to be found in the `Tetra_1.R` example from the `nlsCompare` package. -->
<!-- ?? AB: Are we far enough along to include reference? -->
Here is an abbreviated example:

```{r tetrarun}
time <- c( 1,  2,  3,  4,  6 , 8, 10, 12, 16)
conc <- c( 0.7, 1.2, 1.4, 1.4, 1.1, 0.8, 0.6, 0.5, 0.3)
NLSdata <- data.frame(time,conc)
NLSstart <- c(lrc1 = -2, lrc2 = 0.25, A1 = 150, A2 = 50) # a starting vector (named!)
NLSformula <- conc ~ A1 * exp(-exp(lrc1) * time) + A2 * exp(-exp(lrc2) * time)
tryit <- try(nls(NLSformula, data = NLSdata, start = NLSstart, trace = TRUE))
print(tryit)
```

Note that the sum of squares has been reduced from 61216 to 1.6211, but 
unless `trace` is invoked, the user will not get any information about this.
This almost trivial change to the `nls()` function could be 
useful to R users.
